---
output:
  html_document: default
  pdf_document: default
---
# Week 6: Discrete Probability and Binomial Distribution

## Example 1

On page 249 of the OpenStax textbook, a hospital researcher find number of 
times x the average post-op patient will ring the nurse during a 12-hour 
shift.  The data are the following.

```{r}
x <- c(0, 1, 2, 3, 4, 5)
p <- c(4/50, 8/50, 16/50, 14/50, 6/50, 2/50)
```

The expected value is calculated by multiply each value of the random
variable by its probability, and then adding the products.  

```{r}
mu <- sum(x*p)
mu
```

The variance and standard deviation are defined as follows.
$$
\sigma^{2} = \sum (x-\mu)^{2} \cdot P(x), \quad
\sigma = \sqrt{\sigma^{2}}
$$
Below we implement the formula.

```{r}
v <- sum((x-mu)^2*p)
sqrt(v)
```

We conclude that the mean is 2.32, and the standard deviation is 1.22.

## Example 2

Consider the example on page 256 of the OpenStax textbook, 41% of adult
workers have a high school diploma but do not pursue any further education.
If 20 adult workers are randomly selected, what is the probability
that at most 12 of them have a high school diploma but do not pursue 
further education?

We can use the dbinom function for this problem.  The probabilities for
exactly 11 and 12 are the following.  

```{r}
dbinom(11, 20, 0.41)
dbinom(12, 20, 0.41)
```

We can use the colon operator to create a sequence from 0 to 12, and 
use sum to add the probabilities together.

```{r}
dbinom(0:12, 20, 0.41)
sum(dbinom(0:12, 20, 0.41))
```

The graph of the binomial probability distribution function is the following.

```{r}
plot(0:20, dbinom(0:20, 20, 0.41), type = "h")
```

## Follow Up

Try the exercise on page 258 of the OpenStax textbook: 60% of American
adults prefer saving over spending.  Out of a random sample of 50,
what is the probability that at most 20 adults prefer saving?  

&copy; 2022 Frank Wang 

