---
output:
  pdf_document: default
  html_document: default
---
# Week 9: Confidence Intervals

## Example 1

William S. Goset of the Guinness brewery in Dublin developed a more accurate
way to estimate the population; it involves the Student's t-distribution.  Below 
we compare the normal t-distributions of degrees of freedom of 5 and 15.

```{r}
curve(dnorm, -4, 4, col = "blue")
curve(dt(x, 5), -4, 4, add = TRUE, col = "green")
curve(dt(x, 15), -4, 4, add = TRUE, col = "red")
```

Consider the example on page 457 of the OpenStax textbook: a researcher
measured sensory rates for 15 subjects.  We manually enter the data below, and
find the sample mean and standard deviation.  

```{r}
x <- c(8.6, 9.4, 7.9, 6.8, 8.3, 7.3, 9.2, 9.6, 8.7, 11.4, 10.3, 5.4, 8.1, 5.5, 6.9)
mean(x)
sd(x)
```

To find the 95% confidence interval, we need to find $t_{\alpha/2}$.  The 
degrees of freedom is 14.  

```{r}
qt(0.05/2, 14)
```

Note that qt give the area to the left of the t-score, but in many introductory
statistics textbook $t_{\alpha/2}$ represents the cut on the right tail, 
and in such a case $t_{\alpha/2}=2.145$.  A better notation for the right cut
is $t_{1-\alpha/2}$.

```{r}
qt(1-0.05/2, 14)
```


The lower and upper bounds of the confidence interval are the following.

```{r}
8.2267 - 2.145*1.6722/sqrt(15)
8.2267 + 2.145*1.6722/sqrt(15)
```

We estimate with 95% confidence that the population mean sensory rate
is between 7.30 and 9.15.

It's possible to find the confidence interval directly by using a pre-defined
function.

```{r}
t.test(x)$conf.int
```

## Example 2

On page 459 of the OpenStax textbook, the Human Toxome Project tested 20
newborn infants.  The number of targeted chemicals found in each infant's cord
blood is shown below.

```{r}
x <- c(79, 145, 147, 160, 116, 100, 159, 151, 156, 126,
       137, 83, 156, 94, 121, 144, 123, 114, 139, 99)
mean(x)
sd(x)
```

The critical value for a 90% confidence interval is found in the following.  The
degrees of freedom is 19.  

```{r}
qt(0.1/2, 19)
```

The lower and upper bounds of the confidence interval are below.

```{r}
127.45 - 1.729*25.9645/sqrt(20)
127.45 + 1.729*25.9645/sqrt(20)
```

We estimate with 90% confidence that the mean number of all targeted industrial 
chemicals found in cord blood is between 117.4 and 137.5.  

Again we can use a pre-defined function to obtain the same result.

```{r}
t.test(x, conf.level = 0.9)$conf.int
```

## Follow Up

On page 488 Homework problem 113, six brands of chocolate chip cookies
were randomly selected at the supermarket.  
The grams of fat per serving are: 8, 8, 10, 7, 9, 9.
Construct a 90% confidence interval for the population mean grams
of fat per serving of chocolate chip cookies sold in supermarkets.    

&copy; 2022 Frank Wang 
