---
output:
  html_document: default
  pdf_document: default
---
# Week 10 & 11: Hypothesis Testing

## Example 1

On page 527 of the OpenStax textbook, the National Institute of Standards 
and Technology provides data on conductivity properties of material.  Following are measurements for 11 randomly selected pieces of a particular type of glass.

```{r}
x <- c(1.11, 1.07, 1.11, 1.07, 1.12, 1.08, 0.98, 0.98, 1.02, 0.95, 0.95)
```

Is there convincing evidence that the average conductivity of this type
of glass is greater tan one?  Use a significance level of 0.05.

We find sample mean and standard deviation below.

```{r}
mean(x)
sd(x)
```

The test statistics is the following.
$$
t=\frac{1.04-1}{\frac{0.0659}{\sqrt{11}}}=2.01
$$
We use the pt function to find the p-value.  The degrees of freedom is 51.  

```{r}
pt(2.01, 10)
1-pt(2.01, 10)
```

Because the p-value (p=0.036) is less than our alpha value, we reject the null
hypothesis.  The data support the claim that the mean conductivity level is
greater than one.  

It is possible to use the pre-defined function to reach the same conclusion.

```{r}
t.test(x, mu = 1, alternative = "greater")
```

## Example 2

A researcher measured the body temperatures of a sample of randomly selected
adults.  We read the data file from Professor Nick Horton's website.

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/Normal_temperature.csv"))
head(dat)
```

The sample mean and standard deviation are the following, along with the sample
size.

```{r}
mean(dat$Temp)
sd(dat$Temp)
length(dat$Temp)
```

The conventional wisdom says that "normal" body temperature is 98.6$^{\circ}$F.
Based on this value, the test statistic is
$$
t= \frac{98.285-98.6}{\frac{0.6824}{\sqrt{52}}} = - 3.34
$$
The p-value is below.

```{r}
pt(-3.34, 51)
2*pt(-3.34, 51)
```

For a two-tailed test, the p-value (p=0.0016) is less than a typical $\alpha$ 
value (5%).  We reject the null hypothesis of 98.6; strong evidence
suggests that the mean is not 98.6.  

Again we can use the t.test function for the entire procedure.

```{r}
t.test(dat$Temp, mu = 98.6)
```

## Follow Up

On page 544 of the OpenStax textbook, Homework problem 85, the mean
work week for engineers in a start-up company is believed to be 60 hours.
A  newly hired engineer hopes that it's shorter.  She asked 10 engineers for
the lengths of their mean work weeks, and have the following: 70, 45, 55, 
60, 65, 55, 55, 60, 50, 55.  Should she count on the mean work week to
be shorter than 60 hours?  

&copy; 2022 Frank Wang 

