---
output:
  pdf_document: default
  html_document: default
---
## Titanic Example

This is an example about the passengers and crew aboard the *Titanic* in the book by De Veaux *et al.*  The following lines are to import data from the file `Titanic.csv`.
We can open the data file saved in a remote location; in this case Professor Nicholas Horton's website at https://nhorton.people.amherst.edu/is5/data.  

```{r}
dat <- read.csv(url(
  "https://nhorton.people.amherst.edu/is5/data/Titanic.csv"))
```

We use `head` and `tail` to examine the beginning and the end of the data frame.

```{r}
head(dat)
tail(dat)
```

To create a one-way table of class: 

```{r}
table(dat$Class)
```

For a two-way table of class and "survived",
```{r}
table(dat$Survived, dat$Class)
```

We assign the two-way table to `tbl`:

```{r}
tbl <- table(dat$Survive, dat$Class)
```

To calculate % of overall total, % of row, and % of column, we do the following.

```{r}
prop.table(tbl)
prop.table(tbl, 1)
prop.table(tbl, 2)
```

We can use the above two-way table to create a side-by-side bar chart.  

```{r}
barplot(prop.table(tbl, 2), beside = TRUE, 
        legend = rownames(tbl))
```

Comparing relative frequency bar chart and pie chart:

```{r}
par(mfrow = c(1, 2))
barplot(table(dat$Class)/length(dat$Class), las = 2)
pie(table(dat$Class))
par(mfrow = c(1, 1))
```

For stacked bar chart:

```{r}
tbl2 <- table(dat$Class, dat$Survived)
barplot(tbl2, col = c("orange", "blue", "red", "green"))
legend("topleft", legend = rownames(tbl2), title = "Class", 
       fill = c("orange", "blue", "red", "green"))
```

We display ages of those aboard Titanit using a histogram.

```{r}
hist(dat$Age)
```

