---
output:
  html_document: default
  pdf_document: default
---
# Week 2: Organizing Data

## Example 1

Professor Nick Horton's website contains a data set of student survey 
result.  We use the function read.csv to open the file remotely.  The
head function shows the first part of the dataframe, and names returns 
the variable names

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/Student_survey.csv"))
head(dat)
names(dat)
```

We use the table function to construct the frequency distribution of the
response to the question "Do you believe in God?" in the example below, and
the barplot function to build a bar chart.  

```{r}
tb1 <- table(dat$Do.you.believe.in.God)
tb1
barplot(tb1)
```

A relative frequency table displays percentages or proportions rather than
the counts in each category.  

```{r}
n <- sum(tb1)
n
tb2 <- tb1/n
tb2
barplot(tb2)
```

## Example 2

We analyze students' self rating of their political inclination below.

```{r}
tb3 <- table(dat$Politics.3Cat)
tb3
barplot(tb3)

tb4 <- tb3/n
tb4
barplot(tb4)
```

## Follow Up

Use the method demonstrated above to analyze the question on "How would
you describe your diet?"  The variable name is "Diet".  

&copy; 2022 Frank Wang 

