---
output:
  html_document: default
  pdf_document: default
---
# Week 4: Linear Correlation and Regression

## Example 1

A study of men's health measured 14 body characteristics of 250 men.  We 
import the data from Professor Nick Horton's website.

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/Bodyfat.csv"))
head(dat)
```

To make a scatter plot of body fat percentage and waist size, we can
do either of the following.

```{r}
plot(dat$Waist, dat$Pct.BF)
plot(dat$Pct.BF ~ dat$Waist)
```

To find the least squares line, we use the lm function.

```{r}
fit <- lm(dat$Pct.BF ~ dat$Waist)
summary(fit)
```

From the R output we read the equation
$$
\hat{y} = 1.70 x - 42.73
$$
where $x$ is the waist size and $R^{2}$ value 0.6785.  We add the least 
squares line to the scatter plot.

```{r}
plot(dat$Pct.BF ~ dat$Waist)
abline(fit)
```

## Example 2

A survey was conducted in the United States and 10 countries of Western
Europe to determine the percentage of teenagers who had used marijuana
and other drugs.  The results are below.  

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/Drug_abuse.csv"))
dat
```

We create a scatter plot, and find the least square line.

```{r}
plot(dat$Other.Drugs.... ~ dat$Marijuana....)
fit <- lm(dat$Other.Drugs.... ~ dat$Marijuana....)
summary(fit)
abline(fit)

```

## Follow up

How are fat and protein related on the entire Burger King's menu?  We 
import the data set as shown below.

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/Burger_King_items.csv"))
names(dat)
```

Use the methods demonstrated above to make a scatter plot and find the least
squares line.  Hint: See Wang page 45.  

&copy; 2022 Frank Wang 
