---
output:
  pdf_document: default
  html_document: default
---
# Week 3: Summary Statistics

## Example 1

On page 100 of the OpenStax textbook, a data set shows the heights in inches 
for a class of 40 students.  To enter the data manually, we use the function
c to create a vector.  Below we use the variable name bh for the heights
of boys, and gh for girls.  

```{r}
bh <- c(66, 66, 67, 67, 68, 68, 68, 68, 68, 69, 69, 69, 70, 71, 72, 72, 72, 73, 73, 74)
gh <- c(61, 61, 62, 62, 63, 63, 63, 65, 65, 65, 66, 66, 66, 67, 68, 68, 68, 69, 69, 69)
```

We use the fivenum function to find the five number summary.

```{r}
fivenum(bh)
fivenum(gh)
```

To produce a boxplot, we do the following.

```{r}
boxplot(bh)
boxplot(gh)
```

Boxplots are useful for making a comparision.  We plot both girls' and boys' 
heights side by side.

```{r}
boxplot(bh, gh, names = c("boys", "girls"))
```

We can change the orientation with the option shown below.

```{r}
boxplot(bh, gh, names = c("boys", "girls"), horizontal = TRUE)
```

The sample mean and sample standard deviation can be evaluated using the
mean and sd functions.  

```{r}
mean(bh)
sd(bh)
mean(gh)
sd(gh)
```

## Example 2

A study of men's health measured 14 body characteristics of 250 men.  We 
import the data from Professor Nick Horton's website.

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/Bodyfat.csv"))
head(dat)
```

We use the following method to product a histogram showing the neck sizes of
the 250 men.

```{r}
hist(dat$Neck)
```

The five number summary and box plot for the neck sizes are obtained below.

```{r}
fivenum(dat$Neck)
boxplot(dat$Neck, horizontal = TRUE)
```

For the wrist circumference, see below.

```{r}
hist(dat$Wrist)
fivenum(dat$Wrist)
boxplot(dat$Wrist, horizontal = TRUE)
```

## Follow Up

Consider the bicep circumferences in the data set Bodyfat.

1. Construct a histogram.
2. Find the five number summary.
3. Construct a box plot.
4. Find the sample mean and standard deviation.  

&copy; 2022 Frank Wang 
