---
output:
  html_document: default
  pdf_document: default
---
# Week 8: Sampling Distribution

## Example 1

A large financial institution in NYC has about 5000 people working
at the Wall Street location.  

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/Population_Commute_Times.csv"))
head(dat)
```

We assign x as the commute time, and show the histogram.

```{r}
x <- dat$Commute.Time
hist(x)
```

Let's find the summary statistics.

```{r}
summary(x)
```

The Human Resources Department chose 100 employees and interviewed them
about their commute experience.  Here is a histogram of the 100
responses.

```{r}
y <- sample(x, 100)
hist(y)
summary(y)
```

Students should run these three lines several times and observe the variation
among samples.

We use the computer to simulate 10,000 different random samples of size 100.

```{r}
z <- replicate(10000, mean(sample(x, 100)))
hist(z)
```

We conclude that statistics vary from sample to sample, but most of
the sample means are close to each other around 45 minutes.  The population
mean is 45.4 minutes.  

## Follow Up

Simulate 10,000 different random samples of size 50.  Compare the histogram
of the means of samples of size 50 with that of size 100 above.  

&copy; 2022 Frank Wang 
