---
output:
  html_document: default
  pdf_document: default
---
# Week 5: Probability Topics

## Example 1

Researchers interviewed people who could remember their dreams and recall 
which side they slept on.

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/Nightmares.csv"),
                skip = 1)
head(dat)
```

We can organize the data into a two-way table.

```{r}
table(dat)
```


## Example 2

We can arrange the counts of how many pet-owning OkCupid participants
have dogs, cats, or both.  

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/OKCupid_CatsDogs.csv"),
                skip = 1)
head(dat)
```

To make a two-way table of pets and gender, we do the following.

```{r}
table(dat$CatsDogsBoth, dat$Gender)
```

## Follow Up

The Titanic data set is below.

```{r}
dat <- read.csv(url("https://nhorton.people.amherst.edu/is5/data/Titanic.csv"))
names(dat)
```

Construct a two-way table of class and "survived."  Hint: See Wang page 7.

&copy; 2022 Frank Wang 
